Spatial Reasoning and Data Displays

### 2015-01-11 Paper/Draft1/TestingVisualAptitude.Rnw

This aspect of lineups provides an important tool in the evaluation of graphical findings, in that we can aggregate responses from many individuals to evaluate a single graphic. In addition, however, we can aggregate an individual's score over several lineups to determine how well single individuals perform on the lineup task; data from previous lineup studies suggests that there is significant variation in individual performance as well. This study has the potential to explain some of that variance - if visual skills are important contributors, then perhaps we are simply measuring differences in spatial reasoning ability.
\newtext{
In order to evaluate an individual's overall lineup score, we would subtract a fraction of a point for each question answered incorrectly, and add a full point for each question answered correctly, as shown in 
\ref{eq.scoring1}.

>>>>

\newtext{
This aspect of lineups provides an important tool in the evaluation of graphical findings, in that we can aggregate responses from many individuals to evaluate a single graphic. In addition, however, we can aggregate an individual's score over several lineups to objectively compare individual performance on the lineup task.

In order to evaluate an individual's overall lineup score, we would subtract a fraction of a point for each question answered incorrectly, and add a full point for each question answered correctly, as shown in 
\ref{eq.scoring1}.
